\documentclass{standalone}

%%%%%%%%%% Load Packages %%%%%%%%%%

%%% Required packages and settings  %%%%%
% Geometry package for setting page margins.
%\usepackage[left=2.5cm, right=2.5cm, top=1.5cm, bottom=1.5cm]{geometry}

% Packages for images and figures.
%\usepackage{graphicx} % For including graphics.
%\usepackage{setspace}

%\date{}
%\doublespacing
%\setlength{\parindent}{0pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%opening


\begin{document}

%\maketitle
%\textbf{\large Survey Invitation}


Ever wondered what is really in those Terms and Conditions when you sign up for a social media or online account? Curious about what rights and responsibilities you are agreeing to? Help us make this information easier to understand and more transparent by completing a short online research study. 

My name is Mozammal Hossain. I am a Ph.D. candidate in the Computer Science Department at UNB. I am conducting a short academic survey to explore this very topic, and your input would be incredibly valuable for my research. Participation involves completing a short online survey (10–15 minutes) and will help promote clear and fair software use for everyone. 

To participate or learn more, please click \textbf{here} or contact me at mozammal.hossain@unb.ca. 

Thank you in advance for your time and interest. Your contribution makes my research possible and will help promote clarity and transparency in software use moving forward.


Mozammal Hossain

PhD. Research Student, UNB Faculty of Computer Science 

\textbf{This study was reviewed and is on file as UNB REB XXX-XXXX}

\end{document}
